% This is an example of the `Acknowledgment' section.
% To generate the final document, run latex, build and quick build commands
% on the skeleton-thesis file (not this one)

\chapter*{Acknowledgment}\label{acknowledgment}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}
\vspace{7mm}

The list of who deserves acknowledgment for the thesis laid in front of you is near endless, though at the top of the technical pile rests my advisor and mentor, Prof. Sait Umar.
It's clear that my career in science would have taken a very different trajectory had I not joined this group at Vanderbilt, and his winning combination of patience and knowledge ensured that I come out of my time here a better scientist.
Through his support I was afforded the freedom to explore the science of nuclei without worry, and for that I am extremely grateful.

My committee members deserve praise as well, for they must read the sum total of five years of work and get up to speed quickly.
They've dedicated time they may not have in great supply, so I thank them greatly.

The final group of people who have made the technical work in this thesis possible are my many collaborators who I've had the pleasure of working with throughout the years.
Indeed, their names lie at the top of several chapters and thus deserve more praise than I can give them.
I would also like to thank the numerous colleagues who I have met at workshops, visits, and conferences who have contributed to the science in this thesis.

This thesis also represents a substantial effort of emotional will, spread out over the past 5 years.
First and most immediate, the staff and faculty of the Vanderbilt Physics \& Astronomy Department have done incredible work making a sometimes painful process as smooth as possible.

Next, my friends.
Some of them are also included in the previous offers of grace, though double counting is no sin here.
Be you a relatively new addition like Shanti, or have been around as long as Gavin, you are welcome in my heart and have made my PhD possible.

Finally, my family.
Every moment of my adult life has been the result of the combined effort of my Mom and Dad, along with input from my Nana and countless other family members.
Even the shortest second with my siblings represents a priceless treasure.
I wouldn't be who I am without them (literally), and I am grateful for the support they've provided for my first 27 years.
Here's to many more with them, and everyone one else who has lent a hand in shaping me.



